Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
keeping touch [fixed]

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) needs should be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

@@

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool for keeping touch with students. Also, they are the baseline platform for the development of chatbots to help with the learning process. After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.

>>>>

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

@@

%Why messaging apps are relevant here --> connect to the development of chatbots
Group messaging apps have become a powerful tool to communicate with students. Also, they are the baseline platform for the development of 
chatbots to help with the learning process. After an initial analysis to the answers to the first survey, we realized that there were some prior issues mainly related to the adoption of a technology, chatbots, that generally piggybacks on another, messaging applications. In a technology adoption model, perceived ease of use and perceived usefulness are essential. But it is going to be very difficult for teachers to find {\em chatbots} easy to use if they, previously, do not consider, or simply use, the messaging tools to which they are attached.
